Distributional Regression Forests for Probabilistic Precipitation Forecasting in Complex Terrain

### 2018-10-16 pkg/disttree/inst/draft/rejoinder.Rnw
rejoinder now as .Rnw-file
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/partykit@2330 255f4249-2263-4417-b1ea-8498779e27a7

Former-commit-id: 3720b1820e7da2193c2409d02aacb1f3a4c841d0

\begin{document}
\begin{letter}{
Nicoleta Serban\\
Area Editor\\
The Annals of Applied Statistics}

@@

\begin{center}
\includegraphics[width = .8\textwidth]{topo-GFS.pdf}
\end{center}

@@

\begin{center}
\includegraphics[width = .7\textwidth]{varimp_gb.pdf}
\end{center}

>>>>

\begin{document}
\SweaveOpts{concordance=TRUE}
\begin{letter}{
Nicoleta Serban\\
Area Editor\\
The Annals of Applied Statistics}

@@

\begin{center}
\setkeys{Gin}{width=0.8\textwidth}
<<topography, fig=TRUE, echo=FALSE, height=3.5, width=8>>=

# Preamble
library("sp")
library("raster")
library("ncdf4")
data(StationsTyrol, package = "RainTyrol")
data(MapTyrol, package = "RainTyrol")
# data(MapTyrol_border, package = "RainTyrol")
# Create SpatialPointsDataFrame from station list
sp <- SpatialPointsDataFrame(subset(StationsTyrol,
                                    select=c(lon,lat)),
                             data = subset(StationsTyrol,
                                           select = -c(lon,lat)),
                             proj4string = crs(MapTyrol$RasterLayer))

## plot map of Tyrol with all 95 observations
par(mfrow = c(1, 2), mar = rep(0.1, 4), oma = rep(3, 4))

# limits and axis config
zlim <- c(400, 3900)
xat  <- pretty(coordinates(MapTyrol$RasterLayer)[,1], 5)
yat  <- pretty(coordinates(MapTyrol$RasterLayer)[,2], 5)
cols <- gray.colors(100, start = 0.95, end = 0.05)

# Plotting "real" topography
raster::image(MapTyrol$RasterLayer, col = cols,
              main=NA, ylab = "Latitude", xlab = "Longitude",
              xlim = c(9.8,13.2), ylim = c(46.6, 47.87), zlim = zlim,
              xaxt = "n", yaxt = "n")
box()
plot(MapTyrol$SpatialPolygons, add = TRUE)
points(sp, pch = 19, cex = .5)
axis(side = 1, at = xat); axis(side = 2, at = yat)
mtext(side = 2, line = 2, cex = .8, "Latitude")

# Loading and plotting regular_ll GFS topography
##gfs <- raster("gfs_topo.nc")
##gfs_resampled <- raster::resample(gfs, MapTyrol$RasterLayer)
raster::image(raster("gfs_topo.nc"), col = cols,
              main=NA, ylab = "Latitude", xlab = "Longitude",
              xlim = c(9.8,13.2), ylim = c(46.6, 47.87), zlim = zlim,
              xaxt = "n", yaxt = "n")
box()
plot(MapTyrol$SpatialPolygons, add = TRUE)
points(sp, pch = 19, cex = .5)
axis(side = 1, at = xat); axis(side = 4, at = yat)
mtext(side = 4, line = 2, cex = .8, "Latitude")

mtext(side = 1, line = 2, cex = .8, outer = TRUE, "Longitude")
# Title
mtext(side = 3, line = 1, cex = 1.2, font = 2, outer = TRUE,
      "Comparison of Real Topography and GFS Model Topography")
@
\end{center}

@@

\begin{center}
\setkeys{Gin}{width=0.6\textwidth}
<<varimp_gb, fig=TRUE, echo=FALSE, height=4, width=6>>=
if(file.exists("vimp_crps_gb.rda")){
  load("vimp_crps_gb.rda")
} else {

  nperm <- 50
  library("gamboostLSS")
  library("crch")
  library("scoringRules")
  library("RainTyrol")

  # set function for parallelization
  applyfun <- function(X, FUN, ...) parallel::mclapply(X, FUN, ..., mc.cores = pmax(1, detectCores() - 1))

  # model
  load("Axams_24to4.rda")
  gb <- Axams_24to4$gb

  # data
  data("RainTyrol")
  RainData <- RainTyrol[RainTyrol$station == "Axams", ]
  rownames(RainData) <- c(1:NROW(RainData))

  # learning data: 24 years (1985 - 2008, both inlcuded)
  # testing data: 4 successive years (2009, 2010, 2011, 2012)
  # learndata <- RainData[RainData$year < 2009,]
  testdata <- RainData[RainData$year %in% c(2009, 2010, 2011, 2012),]

  ## compute variable importance for the gamboostLSS object 'gb'

  meancrps <- function(permute = NULL, newdata = testdata) {
    if(!is.null(permute)) newdata[[permute]] <- sample(newdata[[permute]])
    m <- predict(gb, newdata = newdata, parameter = "mu", type = "response")
    s <- predict(gb, newdata = newdata, parameter = "sigma", type = "response")
    mean(crps_cnorm(newdata$robs, location = m, scale = s, lower = 0))
  }

  # apply for all covariates except for dswrf_mean_min and 
  # dswrf_sprd_min (columns 30 and 33) as they are always 0

  risklist <- applyfun(1:nperm, 
                       function(i){
                         set.seed(i)
                         sapply(c(5:29, 31, 32, 34: ncol(testdata)), meancrps)
                       })
  risk <- Reduce("+", risklist) / length(risklist)

  names(risk) <- names(testdata)[c(5:29, 31, 32, 34: ncol(testdata))]
  vimp_crps_gb <- risk - meancrps(newdata = testdata)
  vimp_crps_gb <- sort(vimp_crps_gb, decreasing = TRUE)

  save(vimp_crps_gb, file = "vimp_crps_gb.rda")

}

top10_gb <- vimp_crps_gb[1:10]

par(mar = c(4,10,1,2))
barplot(rev(top10_gb), 
        horiz = TRUE, las = 1, axes = FALSE,
        xlab = "Variable importance: mean decrease in CRPS",
        font.axis = 3, #list(family="HersheySerif", face=3),
        # xlim = c(0,1.1),
        xlim = c(0,0.4),
        names.arg = gsub("pow", "", names(rev(top10_gb))))
axis(1, at = seq(0,1.6,0.1), las = 1, mgp=c(0,1,0))
@
\end{center}
